---
output: github_document
---

[![Build Status](https://travis-ci.org/alastairrushworth/htmldf.svg?branch=master)](https://travis-ci.org/alastairrushworth/htmldf)
[![codecov](https://codecov.io/gh/alastairrushworth/htmldf/branch/master/graph/badge.svg)](https://codecov.io/gh/alastairrushworth/htmldf)


# htmldf

The package `htmldf` contains a single function `html_df()` which accepts a vector of urls as an input and from each will attempt to download each page, extract and parse the html.  The result is returned as a `tibble` where each row corresponds to a document, and the columns contain page attributes and metadata extracted from the html, including:

+ page title
+ inferred language
+ RSS feeds
+ hyperlinks
+ image links
+ twitter, github and linkedin profiles
+ the inferred programming language of any text with code tags
+ page size, generator and server
+ page accessed date
+ page published or last updated dates


Installation and usage
---  

To install the package:

```{r, eval=FALSE}
remotes::install_github('alastairrushworth/htmldf)
```

To use `html_df`
```{r, message=FALSE}
library(htmldf)
library(dplyr)

urlx <- c("https://alastairrushworth.github.io/Visualising-Tour-de-France-data-in-R/",
          "https://www.tensorflow.org/tutorials/images/cnn", 
          "https://www.robertmylesmcdonnell.com/content/posts/mtcars/")
z <- html_df(urlx, show_progress = FALSE)
z
```

Page titles
```{r}
z %>% select(title, url2)
```

RSS feeds
```{r}
z$rss
```

Social profiles
```{r}
z$social
```

Inferred code language
```{r}
z %>% select(code_lang, url2)
```


Comments? Suggestions? Issues?
---  

Any feedback is welcome! Feel free to write a github issue or send me a message on [twitter](https://twitter.com/rushworth_a).




